Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal

### 2020-10-25 Papers/02_Sound_Representation/SoundRepresentation.tex
progress with the paper
added some brief intro

@@

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{06approximation-alto}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Two adjacent pseudo-cycles. The detail view illustrates that $C^0$ and $C^1$ smoothness are maintained in the parametric representation.}
  \label{fig:05approximation-alto}
\end{figure}

>>>>

We aim in providing a method that, with minimal manual interference, is able to reduce a digital wave to a more compact and meaninful representation.

@@

\begin{figure}[ht!]
  \centering
    %  \includegraphics[width=0.9\linewidth]{01signalenvelope}
     \includegraphics{06approximation-alto}
    % \def\svgwidth{\linewidth}
    %\input{01signalenvelope.pdf_tex}
  \caption{Two adjacent pseudo-cycles. The detail view illustrates that $C^0$ and $C^1$ smoothness are maintained in the parametric representation when two reconstructions are stacked horizontally.}
  \label{fig:05approximation-alto}
\end{figure}
